### 2019-04-05 5_evaluation.tex
Tweak text.

Figure~\ref{fig:bytes} shows the performance of Task Bench
implementations with a memory-bound kernel. We measure peak memory
bandwidth of 108 GB/s, which compares favorably with the
OpenMP-enabled STREAM benchmarks~\cite{STREAM} which report betweeen
79 and 90 GB/s.

>>>>

Figure~\ref{fig:bytes} shows the performance of Task Bench
implementations with a memory-bound kernel. We measure peak memory
bandwidth of 108~GB/s, which compares favorably with the
OpenMP-enabled STREAM benchmarks~\cite{STREAM} which report up to 98~GB/s.
